---
title: "Code Ownership in Github Action Workflow files"
output:
  html_document:
    df_print: paged
---

# GA Code Ownership Analysis

```{r message=FALSE}
library(dplyr) 
library(tidyr)
library(stringr)
library(readr) # read csv
library(ggpubr) # combine multiple graphs into one
library(ggplot2)
library(lubridate)
library(Polychrome) # color palette
library(knitr)
library(kableExtra)
library(gridExtra)
```

```{r}
# set working directory
setwd(setwd("~/Documents/GitHub/code-ownership-analysis"))
```

## Import data

```{r message=FALSE, warning=FALSE}
tensorflow <- read_csv("./data/tensorflow_commit_history.csv")
keras <- read_csv("./data/keras_commit_history.csv")
pytorch <- read_csv("./data/pytorch_commit_history.csv")
vscode <- read_csv("./data/vscode_commit_history.csv")
powertoys <- read_csv("./data/PowerToys_commit_history.csv")
react <- read_csv("./data/react_commit_history.csv")
reactNative <- read_csv("./data/react-native_commit_history.csv")
createReactApp <- read_csv("./data/create-react-app_commit_history.csv")
core <- read_csv("./data/core_commit_history.csv")
flutter <- read_csv("./data/flutter_commit_history.csv")
azureDocs <- read_csv("./data/azure-docs_commit_history.csv")
stableDiffusionWebUI <- read_csv("./data/stable-diffusion-webui_commit_history.csv")
nextJs <- read_csv("./data/next.js_commit_history.csv")
langchain <- read_csv("./data/langchain_commit_history.csv")
```

### Check for missing data

When reading the commit data from these files, R will throw warning messages because of missing values. The following code chunk inspects what values are missing.

```{r include=FALSE}
# 1 NA in date
reactNative %>% summarise(across(everything(), ~ sum(is.na(.)))) 
# 2 NA in date
createReactApp %>% summarise(across(everything(), ~ sum(is.na(.)))) 
# 7 NA in date + 6 in message
core %>% summarise(across(everything(), ~ sum(is.na(.)))) 
# 14 NA in date + 2 in message
flutter %>% summarise(across(everything(), ~ sum(is.na(.)))) 
# 4 NA in date + 31 message
azureDocs %>% summarise(across(everything(), ~ sum(is.na(.)))) 
# 7 NA in date + 20 in message
nextJs %>% summarise(across(everything(), ~ sum(is.na(.))))
# 20 NA in date
langchain %>% summarise(across(everything(), ~ sum(is.na(.)))) 
```

## Data preprocessing

### Combine data in a single data frame

Combine the data of all repositories into a single data frame. Here I also create a new column called `repo` to indicate from which repository the data is from.

```{r}
all_repos <- bind_rows(
  tensorflow %>% mutate(repo='tensorflow'), 
  keras %>% mutate(repo='keras'), 
  pytorch %>% mutate(repo='pytorch'),
  vscode %>% mutate(repo='vscode'),
  powertoys %>% mutate(repo='powertoys'),
  react %>% mutate(repo='react'),
  reactNative %>% mutate(repo='reactNative'),
  createReactApp %>% mutate(repo='createReactApp'),
  core %>% mutate(repo='core'),
  flutter %>% mutate(repo='flutter'),
  azureDocs %>% mutate(repo='azureDocs'),
  stableDiffusionWebUI %>% mutate(repo='stableDiffusionWebUI'),
  nextJs %>% mutate(repo='nextJs'),
  langchain %>% mutate(repo='langchain'))
```

### Extract yaml files

Extract yaml commits inside the `.github/workflows` directory. The input data frame needs to be structured so that each row represents a yaml file from a commit. If a commit features multiple yaml files, it is split into multiple rows.

```{r}
# helper function
extract_yaml_files <- function(commits_df){
  yamlFiles <- commits_df %>%
    filter(
      str_starts(file, ".github/workflows/") &
      str_ends(file, ".yml")) %>%
    mutate(file = gsub(".github/workflows/","",file)) %>% # remove path from file name
    mutate(file = gsub(".yml|.yaml","",file)) # remove file ending to shorten the names
  
  return(yamlFiles)
}
```

```{r}
# TensorFlow
tensorflow_yml_commits <- extract_yaml_files(tensorflow) 
# Keras
keras_yml_commits <- extract_yaml_files(keras) 
# Pytorch
pytorch_yml_commits <- extract_yaml_files(pytorch) 
# VScode
vscode_yml_commits <- extract_yaml_files(vscode)
# PowerToys
powertoys_yml_commits <- extract_yaml_files(powertoys)
# React
react_yml_commits <- extract_yaml_files(react)
# React-Native
reactNative_yml_commits <- extract_yaml_files(reactNative)
# Create-React-App
createReactApp_yml_commits <- extract_yaml_files(createReactApp)
# Core
core_yml_commits <- extract_yaml_files(core)
# Flutter
flutter_yml_commits <- extract_yaml_files(flutter)
# Azure-Docs
azureDocs_yml_commits <- extract_yaml_files(azureDocs)
# stableDiffusionWebUI
stableDiffusionWebUI_yml_commits <- extract_yaml_files(stableDiffusionWebUI)
# nextJs
nextJs_yml_commits <- extract_yaml_files(nextJs)
# React
langchain_yml_commits <- extract_yaml_files(langchain)
```

Combine all yml files into a single data frame

```{r}
all_yml_files <- bind_rows(
  tensorflow_yml_commits %>% mutate(repo='tensorflow'),
  keras_yml_commits %>% mutate(repo='keras'),
  pytorch_yml_commits %>% mutate(repo='pytorch'),
  vscode_yml_commits %>% mutate(repo='vscode'),
  powertoys_yml_commits %>% mutate(repo='powertoys'),
  react_yml_commits %>% mutate(repo='react'),
  reactNative_yml_commits %>% mutate(repo='reactNative'),
  createReactApp_yml_commits %>% mutate(repo='createReactApp'),
  core_yml_commits %>% mutate(repo='core'),
  flutter_yml_commits %>% mutate(repo='flutter'),
  azureDocs_yml_commits %>% mutate(repo='azureDocs'),
  stableDiffusionWebUI_yml_commits %>% mutate(repo='stableDiffusionWebUI'),
  nextJs_yml_commits %>% mutate(repo='nextJs'),
  langchain_yml_commits %>% mutate(repo='langchain'),
  )
```

## Functions for creating the plots

### Commit contribution by file

This plot shows the number of authors and commits per file.

```{r}
plot_commit_contribution <- function(df, repoName) {
  # get number of unique values
  ymlFilesCount <- n_distinct(df$file)
  ymlAuthorCount <- n_distinct(df$author)
  # set thresholds
  thresholdFiles <- 10
  thresholdAuthors <- 20
  
  # Filter df to include top 'thresholdFiles' files with most commits, or all if fewer exist
  top_files <- df %>%
      # count occurrences of each file
      count(file, name = "count") %>%
      # sort files by their number of commits
      arrange(desc(count)) %>%
      # use slice_head to get exactly the number of files even if there are ties
      # if number of files exceeds threshold, use threshold as max number of files to plot
      slice_head(n = min(ymlFilesCount, thresholdFiles))
  
  plot_data <- df %>%
    filter(file %in% top_files$file)
  
  plot <- plot_data %>%
    group_by(file, author) %>%
    summarise(count = n()) %>% 
    ggplot(., aes(fill = author, x = reorder(file, count, sum), y = count, label = count)) +  
    geom_bar(position ="stack", stat = "identity") + 
    geom_text(size = 3, position = position_stack(vjust = 0.5)) + 
    labs(
      x = "Yaml Files", 
      y = "Number of Commits", 
      title = paste("Commit Contribution for YAML Files in", repoName),
      # show different text based on number of files in df
      caption = ifelse(ymlFilesCount > thresholdFiles,
        paste("Among ", ymlFilesCount ,"total YAML files, this graph only includes", thresholdFiles , 
              "files with the most commits."),
        paste("Total of", ymlFilesCount ," YAML files from",ymlAuthorCount,"unique authors."))
      )+
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 20, vjust = 1, hjust=1), 
      plot.caption = element_text(hjust=0),
      # display or hide legend based on number of authors
      legend.position = ifelse(
        ymlAuthorCount > thresholdAuthors,
        "none",
        "bottom")
    )
  
  return(plot)
}
# test function with react repo
#plot_commit_contribution(react_yml_commits, "React")
```

### Compare commit contributions of authors

This plot shows the number of commits per author with the color indicating the different files he/she added changes to.

```{r}
plot_author_comparison <- function(df, repoName) {
  # get number of unique values
  ymlFilesCount <- n_distinct(df$file)
  ymlAuthorCount <- n_distinct(df$author)
  # set thresholds
  thresholdFiles <- 20
  thresholdAuthors <- 15
  
  # Filter df to include top 'thresholdFiles' author with most commits, or all if fewer exist
  top_files <- df %>%
      # count occurrences of each author
      count(author, name = "count") %>%
      # sort author by their number of commits
      arrange(desc(count)) %>%
      # use slice_head to get exactly the number of files even if there are ties
      # if number of files exceeds threshold, use threshold as max number of files to plot
      slice_head(n = min(ymlFilesCount, thresholdFiles))
  
  plot_data <- df %>%
    filter(author %in% top_files$author)
  
  plot <- plot_data %>%
    group_by(file, author) %>%
    summarise(count = n()) %>% 
    ggplot(., aes(fill = file, x = reorder(author, count, sum), y = count, label = count)) +  
    geom_bar(position ="stack", stat = "identity") + 
    geom_text(size = 3, position = position_stack(vjust = 0.5)) + 
    labs(
      x = "Authors", 
      y = "Number of Commits", 
      title = paste("Compare commit contribution by authors in", repoName),
      # show different text based on number of files in df
      caption = ifelse(ymlFilesCount > thresholdFiles,
        paste("Among", ymlAuthorCount ,"authors, this graph only includes the", thresholdFiles , 
              "authors with the most commits."),
        paste("Total of", ymlAuthorCount ," Authors who worked on YAML files."))
      ) +
    coord_flip()+
    theme_bw() + 
    theme(plot.caption = element_text(hjust=0),
      # display or hide legend based on number of authors
      legend.position = ifelse(
        ymlAuthorCount > thresholdAuthors,
        "none",
        "bottom")
    )
  
  return(plot)
}
# test function with react repo
#plot_author_comparison(react_yml_commits, "React")
```

### Commit activity as a timeline

This plot shows the number of commits over the time from the first (yaml file) commit in the workflow directory up to the date where the data was fetched.

```{r}
plot_commit_timeline <- function(df, repoName) {
  # get number of unique values
  yearFirstCommit <- min(year(df$date))
  dateFirstCommit <- format(min(as.Date(df$date)), "%B %d, %Y")
  yearLastCommit <- max(year(df$date))
  dateLastCommit <- format(max(as.Date(df$date)), "%B %d, %Y")
  
  totalCommits <- n_distinct(df$hash)
  
  # Calculate max commits on single day
  maxDailyCommit <- df %>%
  count(date = as.Date(date)) %>% # by using as.Date we remove the time from the date
  pull(n) %>%
  max()
  # Calculate number of ticks on y-axis
  maxTicks <- 10
  tickInterval <- ceiling(maxDailyCommit / maxTicks) # round the result to the next bigger int: 2.7 -> 3
  
  plot <- df %>%
    group_by(date) %>%
    summarise(count = n()) %>%
    ggplot(aes(x = as.Date(date), y = count)) + 
    geom_col(color = "#00AFBB", fill="#00AFBB") +
    scale_y_continuous(breaks = seq(0, maxDailyCommit, by = tickInterval), limits = c(0, maxDailyCommit)) +
    labs( 
      x = "Date", 
      y = "Number of Commits", 
      title = paste0("YAML File Commit Activity Over Time in the ",repoName ," Repository (",yearFirstCommit,"-",yearLastCommit,")"),
      caption = paste0("The data represents a total of ",totalCommits, " commits recorded from ",
                      dateFirstCommit, " to ",dateLastCommit,". \nNote: Individual bars represent the total commits per day; gaps indicate days with no recorded activity." )) + 
    theme_bw() + 
    theme(plot.caption = element_text(hjust=0)) 
  
  return(plot)
}
# test function with react repo
#plot_commit_timeline(react_yml_commits, "React")
```

### Ownership map

This plot shows an ownership map where you can see who committed when to a file and who was the owner of it at what point in time.

```{r}
plot_ownership_map <- function(df, repoName) {
  # Create variables to display in plot text
  yearFirstCommit <- min(year(df$date))
  yearLastCommit <- max(year(df$date))
  ymlFilesCount <- n_distinct(df$file)
  ymlAuthorCount <- n_distinct(df$author) # do I need this?
  # set thresholds
  thresholdFiles <- 40
  
  # Filter df to include top 'thresholdFiles' files with most commits, or all if fewer exist
  top_files <- df %>%
      # count occurrences of each file
      count(file, name = "count") %>%
      # sort files by their number of commits
      arrange(desc(count)) %>%
      # use slice_head to get exactly the number of files even if there are ties
      # if number of files exceeds threshold, use threshold as max number of files to plot
      slice_head(n = min(ymlFilesCount, thresholdFiles))
  
  
  # Count the number of commits for each author and file up to each point in time
  commits_cumulative <- df %>%
    filter(file %in% top_files$file) %>% # filter files to reduce number of files in plot
    group_by(file, author) %>%
    arrange(date, .by_group = TRUE) %>%
    mutate(commit_count = row_number()) %>%
    ungroup()
  
  # Initialize the new data frame
  result_df <- data.frame(file = character(), 
                          date = as.Date(character()), 
                          author = character(), 
                          leadingAuthor = character(), 
                          stringsAsFactors = FALSE)
  
  # Loop through each row to determine the leading author
  for(i in 1:nrow(commits_cumulative)) {
    current_file <- commits_cumulative$file[i]
    current_date <- commits_cumulative$date[i]
    
    # Subset the original data frame for the current file and dates up to the current date
    subset_df <- commits_cumulative[commits_cumulative$file == current_file & 
                                      commits_cumulative$date <= current_date, ]
    
    # Determine the leading author (the one with the most commits, and in case of a tie, the most recent)
    leading_author <- subset_df %>%
      group_by(author) %>%
      summarise(commit_count = n(), latest_commit = max(date)) %>%
      arrange(desc(commit_count), desc(latest_commit)) %>%
      slice(1) %>%
      pull(author)
    
    # Append to the result data frame
    result_df <- rbind(result_df, 
                       data.frame(file = current_file, date = current_date, 
                                  author = commits_cumulative$author[i], 
                                  leadingAuthor = leading_author))
  }
  
  # Assign unique colors to each author using a custom color palette
  num_authors <- unique(result_df$author)
  seedcolors <- c(
    "#E63946", "#F4A261", "#2A9D8F", "#D90429", "#E76F51", 
    "#2A6F97", "#F77F00", "#80B918", "#9A031E", "#D62828", 
    "#023E7D", "#5F0F40", "#9E0059", "#F8961E", "#3A0CA3",
    "#E9C46A", "#8D99AE", "#006D77", "#EF476F", "#F72585")
  colors <- createPalette(length(num_authors), seedcolors = seedcolors)
  names(colors) <- num_authors
  
  plot <- result_df %>%
    ggplot(aes(x = date, y = file, group = file)) +
    # Add lines that change color based on the leading author
    geom_line(aes(color = leadingAuthor), linewidth = 1, alpha = 1) +
    # Add points for each commit
    geom_point(aes(color = author), size = 3, alpha = 0.6) +
    # Set the colors for the authors
    scale_color_manual(values = colors) +
    # Adjust y-axis to show truncated file names
    scale_y_discrete(labels = function(x) sapply(x, function(y) {
      # shorten all file names longer than 10 characters
      ifelse(nchar(y) > 10, paste0(substr(y, 1, 10), "..."), y)
    })) +
    labs( 
      x = "Date", 
      y = "Files", 
      color = "Authors",
      title = paste0("Ownership Map of YAML Files from ",repoName ," Repository (",yearFirstCommit,"-",yearLastCommit,")"), 
      caption = ifelse(ymlFilesCount > thresholdFiles,
        paste0("From a total of ", ymlFilesCount ," YAML files, this graph only includes ", thresholdFiles , 
              " files with the most commits. \n  Line colors denote the current leading contributor (owner) for each file."),
        paste0("Total of ", ymlFilesCount, " YAML files. Line colors denote the current leading contributor (owner) for each file."))) + 
    theme_bw() + 
    theme(
      legend.position = "none", # hide the legend for spacing reasons
      #legend.box.just = "left",
      # Remove top margin of legend
      #legend.margin = margin(t = 0, unit = "cm"), 
      # Shift legend box to the left
      #legend.box.margin = margin(l = -3, unit = "cm"), 
      # Shift caption to the left
      plot.caption = element_text(hjust = -0.1, vjust = 1))# +  
    #guides(color=guide_legend(ncol=7))
  
  return(plot)
}
# test function with react repo
#plot_ownership_map(react_yml_commits, "React")
```

### Ownership evolution of single file

Create similar plot as the ownership map but only for a single file and display additions and deletions for each commit. This function takes a df from the hole repo together with its name, as well as the name of the file of interest as input.

```{r}
plot_file_evolution <- function(df, repoName, fileName) {
  # Filter df for specific file
  filtered_df <- df %>% filter(file==fileName)
  
  # get number of unique values
  ymlFilesCount <- n_distinct(filtered_df$file)
  ymlAuthorCount <- n_distinct(filtered_df$author)
  commitCount <- nrow(filtered_df)
  
  # set thresholds
  thresholdCommits <- 40
  
  # Assign unique colors to each author
  author_colors <- setNames(rainbow(length(unique(filtered_df$author))), unique(filtered_df$author))
  
  plot_data <- filtered_df %>%
    mutate(net_change = as.numeric(additions) - as.numeric(deletions)) %>%
    arrange(date, hash) %>%
    mutate(commit_order = row_number())
  
  plot <- plot_data %>%
    ggplot(aes(x = commit_order, 
               y = net_change, 
               fill = ifelse(net_change > 0, 'Positive', 'Negative'))) +
    geom_bar(position ="stack", stat = "identity", width = 1) + 
    scale_fill_manual(values = c("Positive" = "darkgreen", "Negative" = "darkred")) +
    scale_x_continuous(name = "Commit Sequence", breaks = NULL) + # remove x-axis breaks
    scale_y_continuous(name = "Lines Changed", 
                       breaks = scales::pretty_breaks(n = 10), 
                       labels = scales::comma) +
    geom_bar(aes(color=factor(author)), position="stack", stat="identity", show.legend = FALSE) + # Add border color
    scale_color_manual(values = author_colors) +
    geom_hline(yintercept = 0) + # Add zero line
    labs(
      title = paste0("Commit Contributions for file \"", fileName,"\" in ", repoName),
      # show different text based on number of files in df
      caption = paste("Total of", commitCount ," commits from",ymlAuthorCount,"unique authors.")) +
    theme_bw() + 
    theme(axis.ticks.x = element_blank(), 
      plot.caption = element_text(hjust=0),
      legend.position = "none")
  
  return(plot)
}
# test function with react repo
#plot_file_evolution(react_yml_commits, "React", "commit_artifacts")
```

# Repository Analysis

## Overview

```{r}
# Summarize all repository data
repo_summary <- all_repos %>%
  # remove commits without commit date
  filter(!is.na(date)) %>%
  group_by(repo) %>%
  summarize(
    "commits" = n_distinct(hash),
    "authors" = n_distinct(author),
    "first commit" = min(as.Date(date)),
    "last commit" = max(as.Date(date))
  )

# Summarize YAML specific data
yaml_summary <- all_yml_files %>%
  # remove commits without commit date
  filter(!is.na(date)) %>%
  group_by(repo) %>%
  summarize(
    yml_commits = n(),
    yml_authors = n_distinct(author),
    "first yml commit" = min(as.Date(date))
  )

# Combine summaries
final_table <- left_join(repo_summary, yaml_summary, by = "repo") %>%
  select(repo, "commits", "authors", yml_commits, yml_authors, "first commit", "last commit", "first yml commit") %>%
  arrange(desc(commits))

# Add a row for total sums
totals <- final_table %>%
  summarize(
    repo = "Total",
    "commits" = sum(commits, na.rm = TRUE) %>% format(big.mark = "'", scientific = FALSE),
    "authors" = sum(authors, na.rm = TRUE) %>% format(big.mark = "'", scientific = FALSE),
    yml_commits = sum(yml_commits, na.rm = TRUE) %>% format(big.mark = "'", scientific = FALSE),
    # get total unique authors not total authors
    yml_authors = sum(yml_authors, na.rm = TRUE) %>% format(big.mark = "'", scientific = FALSE),
    "first commit" = "",
    "last commit" = "",
    "first yml commit" = ""
  )

# Append totals row to the final table
final_table_with_totals <- rbind(final_table, totals)

# Create the table
kable(final_table_with_totals, align = "c",caption = "Repository Summary")
```

### Authors who worked on multiple repos

This table shows 3645 authors who worked on more than one of the repositories that I collected the data from. These people (and bots) committed changes to yml files in the workflow directory of multiple repositories.

```{r message=FALSE}
authors_with_multiple_repos <- all_repos %>%
  group_by(author) %>%
  summarise(numRepos = n_distinct(repo)) %>%
  filter(numRepos >1) %>%
  left_join(all_repos, by = "author") %>%
  group_by(author, numRepos) %>%
  summarise(repositories = paste(unique(repo), collapse = ", ")) %>%
  arrange(desc(numRepos))

# Create the table showing the top 20 auhtors who worked on the most repositories
kable(head(authors_with_multiple_repos,20), align = "c",caption = "Repository Summary")

```

## TensorFlow

### Commit contribution by file and author

```{r}
plot_commit_contribution(tensorflow_yml_commits, "TensorFlow")
```

### Compare contribution by author

```{r}
plot_author_comparison(tensorflow_yml_commits, "TensorFlow")
```

### Commit activity over time

```{r}
plot_commit_timeline(tensorflow_yml_commits, "TensorFlow")
```

### Ownership Map

```{r}
plot_ownership_map(tensorflow_yml_commits, "TensorFlow")
```

### Ownership evolution of single file

```{r}
plot_file_evolution(tensorflow_yml_commits, "TensorFlow", "arm-ci")
```

## Keras

### Commit contribution by file and author

```{r}
plot_commit_contribution(keras_yml_commits, "Keras")
```
### Compare contribution by author

```{r}
plot_author_comparison(keras_yml_commits, "Keras")
```

### Commit activity over time

```{r}
plot_commit_timeline(keras_yml_commits, "Keras")
```

### Ownership Map

```{r}
plot_ownership_map(keras_yml_commits, "Keras")
```

### Ownership evolution of single file

```{r}
plot_file_evolution(keras_yml_commits, "Keras", "actions")
```

## Pytorch

### Commit contribution by file and author

```{r}
plot_commit_contribution(pytorch_yml_commits, "Pytorch")
```

### Compare contribution by author

```{r}
plot_author_comparison(pytorch_yml_commits, "Pytorch")
```

### Commit activity over time

```{r}
plot_commit_timeline(pytorch_yml_commits, "Pytorch")
```

### Ownership Map

```{r}
plot_ownership_map(pytorch_yml_commits, "Pytorch")
```

### Ownership evolution of single file

```{r}
plot_file_evolution(pytorch_yml_commits, "Pytorch", "_win-test")
```

## VScode

### Commit contribution by file and author

```{r}
plot_commit_contribution(vscode_yml_commits, "VS Code")
```

### Compare contribution by author

```{r}
plot_author_comparison(vscode_yml_commits, "VS Code")
```

### Commit activity over time

```{r}
plot_commit_timeline(vscode_yml_commits, "VS Code")
```

### Ownership Map

```{r}
plot_ownership_map(vscode_yml_commits, "VS Code")
```

### Ownership evolution of single file

```{r}
plot_file_evolution(vscode_yml_commits, "VS Code", "ci")
```

## PowerToys

### Commit contribution by file and author

```{r}
plot_commit_contribution(powertoys_yml_commits, "Powertoys")
```

### Compare contribution by author

```{r}
plot_author_comparison(powertoys_yml_commits, "Powertoys")
```

### Commit activity over time

```{r}
plot_commit_timeline(powertoys_yml_commits, "Powertoys")
```

### Ownership Map

```{r}
plot_ownership_map(powertoys_yml_commits, "Powertoys")
```

### Ownership evolution of single file

```{r}
plot_file_evolution(powertoys_yml_commits, "Powertoys", "package-submissions")
```

## React

### Commit contribution by file and author

```{r}
plot_commit_contribution(react_yml_commits, "React")
```

### Compare contribution by author

```{r}
plot_author_comparison(react_yml_commits, "React")
```

### Commit activity over time

```{r}
plot_commit_timeline(react_yml_commits, "React")
```

### Ownership Map

```{r}
plot_ownership_map(react_yml_commits, "React")
```

### Ownership evolution of single file

```{r}
plot_file_evolution(react_yml_commits, "React", "devtools_check_repro")
```

## React-Native

### Commit contribution by file and author

```{r}
plot_commit_contribution(reactNative_yml_commits, "React Native")
```

### Compare contribution by author

```{r}
plot_author_comparison(reactNative_yml_commits, "React Native")
```

### Commit activity over time

```{r}
plot_commit_timeline(reactNative_yml_commits, "React Native")
```

### Ownership Map

```{r}
plot_ownership_map(reactNative_yml_commits, "React Native")
```

### Ownership evolution of single file

```{r}
plot_file_evolution(reactNative_yml_commits, "React Native", "on-issue-labeled")
```

## Create-React-App

### Commit contribution by file and author

```{r}
plot_commit_contribution(createReactApp_yml_commits, "Create-React-App")
```

### Compare contribution by author

```{r}
plot_author_comparison(createReactApp_yml_commits, "Create-React-App")
```

### Commit activity over time

```{r}
plot_commit_timeline(createReactApp_yml_commits, "Create-React-App")
```

### Ownership Map

```{r}
plot_ownership_map(createReactApp_yml_commits, "Create-React-App")
```

### Ownership evolution of single file

```{r}
plot_file_evolution(createReactApp_yml_commits, "Create-React-App", "build")
```

## Core

### Commit contribution by file and author

```{r}
plot_commit_contribution(core_yml_commits, "Core")
```

### Compare contribution by author

```{r}
plot_author_comparison(core_yml_commits, "Core")
```

### Commit activity over time

```{r}
plot_commit_timeline(core_yml_commits, "Core")
```

### Ownership Map

```{r}
plot_ownership_map(core_yml_commits, "Core")
```

### Ownership evolution of single file

```{r}
plot_file_evolution(core_yml_commits, "Core", "builder")
```

## Flutter

### Commit contribution by file and author

```{r}
plot_commit_contribution(flutter_yml_commits, "Flutter")
```

### Compare contribution by author

```{r}
plot_author_comparison(flutter_yml_commits, "Flutter")
```

### Commit activity over time

```{r}
plot_commit_timeline(flutter_yml_commits, "Flutter")
```

### Ownership Map

```{r}
plot_ownership_map(flutter_yml_commits, "Flutter")
```

### Ownership evolution of single file

```{r}
plot_file_evolution(flutter_yml_commits, "Flutter", "scorecards-analysis")
```

## Azure Docs

### Commit contribution by file and author

```{r}
plot_commit_contribution(azureDocs_yml_commits, "Azure Docs")
```

### Compare contribution by author

```{r}
plot_author_comparison(azureDocs_yml_commits, "Azure Docs")
```

### Commit activity over time

```{r}
plot_commit_timeline(azureDocs_yml_commits, "Azure Docs")
```

### Ownership Map

```{r}
plot_ownership_map(azureDocs_yml_commits, "Azure Docs")
```

### Ownership evolution of single file

```{r}
plot_file_evolution(azureDocs_yml_commits, "Azure Docs", "stale")
```

## StableDiffusionWebUI

### Commit contribution by file and author

```{r}
plot_commit_contribution(stableDiffusionWebUI_yml_commits, "StableDiffusionWebUI")
```

### Compare contribution by author

```{r}
plot_author_comparison(stableDiffusionWebUI_yml_commits, "StableDiffusionWebUI")
```

### Commit activity over time

```{r}
plot_commit_timeline(stableDiffusionWebUI_yml_commits, "StableDiffusionWebUI")
```

### Ownership Map

```{r}
plot_ownership_map(stableDiffusionWebUI_yml_commits, "StableDiffusionWebUI")
```

### Ownership evolution of single file

```{r}
plot_file_evolution(stableDiffusionWebUI_yml_commits, "StableDiffusionWebUI", "python-package-conda")
```

## Next.Js

### Commit contribution by file and author

```{r}
plot_commit_contribution(nextJs_yml_commits, "Next.Js")
```

### Compare contribution by author

```{r}
plot_author_comparison(nextJs_yml_commits, "Next.Js")
```

### Commit activity over time

```{r}
plot_commit_timeline(nextJs_yml_commits, "Next.Js")
```

### Ownership Map

```{r}
plot_ownership_map(nextJs_yml_commits, "Next.Js")
```

### Ownership evolution of single file

```{r}
plot_file_evolution(nextJs_yml_commits, "Next.Js", "build_test_deploy")
```

## Langchain

### Commit contribution by file and author

```{r}
plot_commit_contribution(langchain_yml_commits, "Langchain")
```

### Compare contribution by author

```{r}
plot_author_comparison(langchain_yml_commits, "Langchain")
```

### Commit activity over time

```{r}
plot_commit_timeline(langchain_yml_commits, "Langchain")
```

### Ownership Map

```{r}
plot_ownership_map(langchain_yml_commits, "Langchain")
```

### Ownership evolution of single file

```{r}
plot_file_evolution(langchain_yml_commits, "Langchain", "codespell")
```